---
title: "Covid19 status in India as of 24 April 2020"
author: "Rohit Dnyansagar"
date: "4/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, load_libraries, warning=FALSE, message=F}

# Load necessary packages
pacman::p_load(tidyverse, geofacet, hrbrthemes)

```

## Read data
```{r  message=F}
india_covid <- read_csv(file.path(getwd(), "data", "Covid19_24Apr2020.csv"), col_names = T)

```

## Clean column names

```{r}

india_covid_clean <-  india_covid %>% 
  dplyr::rename(State = `Name Of State / UT`, 
         Total_cases = `Total Confirmed Cases`,
         Cured = `Cured/Discharged/Migrated`,
         Id = `S. No.`,
         Dead = Death) %>% 
  mutate(State = ifelse(State == "Telengana", "Telangana", State )) %>% 
  dplyr::select(-c( "Id", "Date" ,"DateTime"))
```

```{r}
india_with_uts <- data.frame(
  row = c(1, 2, 2, 2, 2, 3, 3, 3, 3, 3, 3, 3, 4, 4, 4, 4, 4, 4, 4, 5, 5, 5, 5, 5, 6, 6, 6, 7, 7, 9, 9, 9, 9, 9, 9, 9),
  col = c(3, 8, 3, 2, 4, 7, 5, 3, 8, 2, 6, 4, 4, 1, 3, 2, 8, 7, 5, 2, 8, 4, 3, 7, 4, 2, 3, 3, 4, 1, 2, 3, 4, 5, 6, 7),
  code = c("JK", "AR", "HP", "PB", "UK", "AS", "BR", "HR", "NL", "RJ", "SK", "UP", "CG", "GJ", "JH", "MP", "MN", "ML", "WB", "MH", "MZ", "OD", "TS", "TR", "AP", "GA", "KA", "KL", "TN", "AN", "CH", "DD", "DL", "LA", "LD", "PY"),
  name = c("Jammu and Kashmir", "Arunachal Pradesh", "Himachal Pradesh", "Punjab", "Uttarakhand", "Assam", "Bihar", "Haryana", "Nagaland", "Rajasthan", "Sikkim", "Uttar Pradesh", "Chhattisgarh", "Gujarat", "Jharkhand", "Madhya Pradesh", "Manipur", "Meghalaya", "West Bengal", "Maharashtra", "Mizoram", "Odisha", "Telangana", "Tripura", "Andhra Pradesh", "Goa", "Karnataka", "Kerala", "Tamil Nadu", "Andaman and Nicobar Islands", "Chandigarh", "Dadra and Nagar Haveli and Daman and Diu", "Delhi", "Ladakh", "Lakshadweep", "Puducherry"),
  stringsAsFactors = FALSE
)
```


## Map clened data using facet_geo
### Plot is big so cannot view in markdown. 
### Run this block code in console and view the plot fullscreen
```{r}
  
india_covid_clean %>% 
  gather("Stat", "Value", -State) %>% 
  ggplot(aes(x = Stat, y = Value, fill = Stat)) +
  geom_col(position = "dodge") + 
  theme_ipsum() + coord_flip() + 
  scale_fill_ipsum()+ theme(legend.title = element_blank()) +
  labs(x = "", y ="", title = "Corona status per Indian state ") +
  facet_geo(~ State, grid = india_with_uts) 

 
```

## Union territories need to be considered separately

facet_geo at this moment do not include Union territories on India. This would be abig issue as it excludes a major hub of Covid and thus needs to be considered separately. Also for some wierd reason it does not have Telangana


```{r}
uts <- c("Andaman and Nicobar Islands", "Chandigarh", "Delhi", "Ladakh", "Puducherry", "Telengana")
india_covid_clean %>% 
  filter(State %in% uts) %>% 
  gather("Stat", "Value", -State) %>% 
  ggplot(aes(x = Stat, y = Value, fill = Stat)) +
  geom_col(position = "dodge") + 
  theme_ipsum() + coord_flip() + 
  scale_fill_ipsum()+ theme(legend.title = element_blank(),
                            axis.text.x = element_text(angle = 45)) +
  labs(x = "", y ="", title = "Corona status Indian UTs and Telangana ") +
  facet_wrap(~State, ncol = 3)

```

## Conclusion 
The india_grid1 and india_grid2 in the facet_geo needs an update as to properly represent current Indian states and union territories.


#
#

#
