---
title: "Covid19 status in India as of 24 April 2020"
author: "Rohit Dnyansagar"
date: "4/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, load_libraries, warning=FALSE, message=F}

# Load necessary packages
pacman::p_load(tidyverse, geofacet, hrbrthemes)

```

## Read data
```{r  message=F}
india_covid <- read_csv(file.path(getwd(), "data", "Covid19_24Apr2020.csv"), col_names = T)

```

## Clean column names

```{r}

india_covid_clean <-  india_covid %>% 
  rename(State = `Name Of State / UT`, 
         Total_cases = `Total Confirmed Cases`,
         Cured = `Cured/Discharged/Migrated`,
         Id = `S. No.`,
         Dead = Death) %>% select(-c( "Id", "Date" ,"DateTime"))
```



## Map clened data using facet_geo
### Plot is big so cannot view in markdown. 
### Run this block code in console and view the plot fullscreen
```{r}
  
india_covid_clean %>% 
  gather("Stat", "Value", -State) %>% 
  ggplot(aes(x = Stat, y = Value, fill = Stat)) +
  geom_col(position = "dodge") + 
  theme_ipsum() + coord_flip() + 
  scale_fill_ipsum()+ theme(legend.title = element_blank()) +
  labs(x = "", y ="", title = "Corona status per Indian state ") +
  facet_geo(~ State, grid = "india_grid1") 

 
```

## Union territories need to be considered separately

facet_geo at this moment do not include Union territories on India. This would be abig issue as it excludes a major hub of Covid and thus needs to be considered separately. Also for some wierd reason it does not have Telangana


```{r}
uts <- c("Andaman and Nicobar Islands", "Chandigarh", "Delhi", "Ladakh", "Puducherry", "Telengana")
india_covid_clean %>% 
  filter(State %in% uts) %>% 
  gather("Stat", "Value", -State) %>% 
  ggplot(aes(x = Stat, y = Value, fill = Stat)) +
  geom_col(position = "dodge") + 
  theme_ipsum() + coord_flip() + 
  scale_fill_ipsum()+ theme(legend.title = element_blank(),
                            axis.text.x = element_text(angle = 45)) +
  labs(x = "", y ="", title = "Corona status Indian UTs and Telangana ") +
  facet_wrap(~State, ncol = 3)

```

## Conclusion 
The india_grid1 and india_grid2 in the facet_geo needs an update as to properly represent current Indian states and union territories.


#
#

#
